\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-05-06 paper/paper/paper.tex
removed 'the authors'

Overall, the authors expect such a test to provide a concrete and detailed analysis on the Physical, Weigand, RFID, Bluetooth, and Networking stacks embedded in the device.  Such a test would outline how these protocols work on a device, and provide concrete analysis of potential vulnerabilities and weaknesses found in the implementation.

\section{Conclusions}
Throughout this paper, the authors have discussed how to design a testing framework for attacking modern electronic locking technologies.  The authors listed out different types of attacks that could be run against a bluetooth-enabled locking solution.  Bluetooth attacks were discussed, along with RFID attacks, and the cryptographic attacks underneath both attack vectors.

>>>>

Overall, we expect such a test to provide a concrete and detailed analysis on the Physical, Weigand, RFID, Bluetooth, and Networking stacks embedded in the device.  Such a test would outline how these protocols work on a device, and provide concrete analysis of potential vulnerabilities and weaknesses found in the implementation.

\section{Conclusions}
Throughout this paper, we have discussed how to design a testing framework for attacking modern electronic locking technologies.  We listed out different types of attacks that could be run against a bluetooth-enabled locking solution.  Bluetooth attacks were discussed, along with RFID attacks, and the cryptographic attacks underneath both attack vectors.
